\vskip-0.6in Trade Agreements in the Shadow of Lobbying\protect\footnote{Formerly circulated under the title ``Trade Agreements, Lobbying and Separation of Powers''}

### 2016-01-31 draft.tex
add subsections to sec:model
move obvious text into sec:basic
replace extensive form code with references to game-tree.tex, comment preamble from game-tree.tex

\section{The Model}
\label{sec:model}
\textbf{I begin by describing the basic economic setting within which trade occurs. It is a three-good model with two countries: home (no asterisk) and foreign (asterisk). In each country, preferences are linear in good $N$, which is denoted the numeraire, while the demand functions for $X$ and $Y$ are assumed strictly decreasing and twice continuously differentiable. Further, the demand functions for $X$ and $Y$ are taken to be identical and denoted $D(P_i)$ in home and $D(P_i^*)$ in foreign. $P_i$ denotes the home price of good $i \in \left\{N,X,Y\right\}$ and $P_i^*$ denotes the foreign price of good $i$.}

@@

\begin{figure}
\begin{center}
\begin{tikzpicture}[scale=1.5,font=\footnotesize, grow=right]
% Specify spacing for each level of the tree
\tikzstyle{level 1}=[level distance=10mm,sibling distance=10mm]
\tikzstyle{level 2}=[level distance=10mm,sibling distance=10mm]
% The Tree
\node(0)[solid node,label=above:{$E,E^*$}]{} 
child{node(1)[solid node,label=below:{$0$}]{}
}
child{[white] node(2)[solid node,xshift=12]{}  %note that you need to adjust the yshift if you change the sibling distance
child{[black] node(4)[solid node,label=below:{$0$}]{}
}
child{[white] node(7)[hollow node,xshift=12]{}  %note that you need to adjust the yshift if you change the sibling distance
child{[black] node(9)[solid node,label=below:{$0$}]{} }
child{[black] node(11)[solid node,label=above:{$\infty$}]{} }
 edge from parent node[black, xshift=23]{$e_b$} %note that you need to adjust the yshift if you change the level distance
}
child{[black] node(6)[solid node,label=above:{$\infty$}]{}}
 edge from parent node[black, xshift=23]{$\bta$} %note that you need to adjust the yshift if you change the level distance
}
child{node(3)[solid node,label=above:{$\infty$}]{}
}
;
% information set
    \draw[solid,bend right](1)to(3);
		\draw[solid,bend right](4)to(6);
		\draw[solid,bend right](9)to(11);

\end{tikzpicture}

\end{center}
\caption{Extensive Form\label{fig:ext}}
\end{figure}

>>>>

\section{The Model}
\label{sec:model}

\subsection{The Basic Setup}
\label{sec:basic}
\textbf{I begin by describing the basic economic setting within which trade occurs. It is a three-good model with two countries: home (no asterisk) and foreign (asterisk). In each country, preferences are linear in good $N$, which is denoted the numeraire, while the demand functions for $X$ and $Y$ are assumed strictly decreasing and twice continuously differentiable. Further, the demand functions for $X$ and $Y$ are taken to be identical and denoted $D(P_i)$ in home and $D(P_i^*)$ in foreign. $P_i$ denotes the home price of good $i \in \left\{N,X,Y\right\}$ and $P_i^*$ denotes the foreign price of good $i$.}

@@

\subsection{Preferences}
\label{sec:pref}

\subsection{Information and Equilibrium Selection}
\label{sec:info}

\subsection{Modeling Choices}
\label{sec:choices}

\begin{figure}
	\begin{center}
		\input{game-tree.tex}
	\end{center}
	\caption{Extensive Form\label{fig:ext}}
\end{figure}
